Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
minor

A major challenge with integration from multiple sources is coreference consolidation, or combining representations that co-refer to the same entity into one.  For example, consolidating one's friends from Facebook, Google+, and LinkedIn, one might quickly want to de-duplicate and combine friends that use multiple services so that they each have one representation.  Although we considered a way to do this automatically, PS.2 revealed no way to reliably identify co-referring instances; due to a lack of standard URIs across social networks, identifiers used by each network were system-specific and inconsistent. Thus, we sought to make instead make it user-driven, and easy to do manually.

@@

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge the task performance is the number of different data sources consulted during the trial; our rationale for this metric was that more informed decisions derived from more thorough consideration of available data. In this metric, participants used an average of 88\% ($SD=0.13$) of data sources provided in the DP case, compared to 80\% ($SD=0.18$)in the standard interface, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance ($F(1,19)=0.04$ $p\approx0.10$).

>>>>

A major challenge with integration from multiple sources is coreference consolidation, or combining representations that co-refer to the same entity into one.  For example, consolidating one's friends from Facebook, Google+, and LinkedIn, one might quickly want to de-duplicate and combine friends that use multiple services so that they each have one representation.  Although we considered a way to do this automatically, PS.2 revealed no way to reliably identify co-referring instances; due to a lack of standard URIs across social networks, identifiers used by each network were system-specific and inconsistent. Thus, we sought to instead make it user-driven, and easy to perform manually.

@@

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge the task performance is the number of different data sources consulted during the trial; our rationale for this metric was that more informed decisions derived from more thorough consideration of available data. In this metric, participants used an average of 88\% ($SD=0.13$) of data sources provided in the DP case, compared to 80\% ($SD=0.18$) in the control condition, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance ($F(1,19)=0.04$ $p < 0.15$).
